\section{Primitives}
\label{sec:primitive}
\fixme{Need to find better names.
\begin{enumerate}
\item Infrastructure Component: A single piece of software (say a cache) situated at the network edge.
\item Application edge: The collection of all software at the edge (the thing kind of dictated by the abstract invocation?
\end{enumerate}
}

\fixme{Maybe merge this with Interfaces}

\begin{outline}
%\1 Unless otherwise stated primitives are per-tennant. Coordinator is the only exception to this rule.
\1 Coordinator
    \2 Interface for providing information to the network.
    \2 Responsible for:
        \3 Accepting abstract invocations and returning a handle.
        \3 Accepting metadata for an invocation handle.
        \3 Disseminating invocations and metadata.
        \3 Instantiating tenant invocations at the network edge.
    \2 The only service that is not per-tenant. 

\1 Discovery
    \2 Local name lookup service: translates a name in the tenant namespace to the address of a nearby provider.
    \2 Is edge aware (so finds services connected to the same edge).
    \2 Can potentially mark entries as requiring authentication: these entries are only visible to clients that have somehow been authenticated.
    \2 We allow clients to be registered as destination, this is useful for things where peer-to-peer connection is desirable.
    \2 Glues services together.
    \2 As an optimization discovery can be eliminated
        \3 Registering a client proactively returns an address
        \3 The address is used for all communications thereafter.
        \3 Main difference:
            \4 Proactive discovery reduces the latency to access services (by at least 1 RTT). 
            \4 Discovering on demand provides greater flexibility: 

\1 Other Infrastructure Components
    \2 Per-tenant services implemented at the edge.
    \2 Some of these are common enough that should be implemented by carriers.
    \2 Some examples
        \3 Caches
        \3 Rendezvous proxies
        \3 Transcoders
        \3 Others
    \2 How to ensure safety
        \3 Isolation: Just use VMs or other existing things.
        \3 Network safety: Limit where traffic can be sent, rate limit to ensure network is not affected

\eat{\1 Things to consider when writing a new edge service.
    \2 Configuration must be location and ``scale'' agnostic.
        \3 In particular should not assume that only a certain number of instances are being run.
        \3 No assumption about where this edge service is being run, no hard coded addresses etc.
    \2 Send requests to other edge services by name.
        \3 A natural consequence of being location agnostic.
    \2 Should not depend on any implicit consistency between edge instances.
        \3 Can explicitly choose to synchronize content using a central server or other mechanism.
        \3 Must not assume anything about latency between instances, instances might be far away geographically.
        \3 In particular this means that client data should only be cached at the edge in most cases
            \4 Mobility would require synchronizing user data somehow.
        \3 \notepanda{Consistency seems hard to provide across different types of services}
    \2 The edge service might be affected by both soft state and configuration.
    \2 \fixme{Figure out other requirements for edge services}
}

\eat{\1 Discovery: Global/Local
    \2 Nameservice: glue holding this all together.
    \2 Local discovery: add local information to normal name service.
    \2 Per-tenant: avoids name collision
        \3 Safety.
    \2 Allow lookups protected by authentication
\1 Edge services
    \2 A variety of per-tenant services implemented at the edge.
        \3 Introduce why this is reasonable: edge has plenty of cores, etc.
        \3 Per-tenant implies safe (cannot affect other tenants).
        \3 At edge, so network protected by the same mechanism as now.
    \2 Examples
        \3 Caches
        \3 Rendezvous proxies (SIP proxies, other things).
        \3 Transcoders
        \3 Application-specific
        \3 etc.
}
\end{outline}